### 2015-03-02 fundamentals/impl.tex
addresses concern from Erich ' is there a distinction between agents and actors?  Using both terminologies may confuse people'

\Cyclus implements an \acrlong{ABM} paradigm. \gls{ABM} enables model
development to take place at an agent level rather than a system level. In the
nuclear fuel cycle context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the
behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in
the same simulation without any shared knowledge, allowing modelers to
construct a simulation from building blocks of many types and origins.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

>>>>

\Cyclus implements an \acrlong{ABM} paradigm. \gls{ABM} enables model
development to take place at an agent level rather than a system level. In the
nuclear fuel cycle context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the
behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide agents in the simulation.  The two archetype libraries can be used in
the same simulation without any shared knowledge, allowing modelers to
construct a simulation from building blocks of many types and origins.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.
